% LaTeX file for resume 
% This file uses the resume document class (res.cls)
\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download
% helvetica.sty) \usepackage{newcent}   % uses new century schoolbook postscript font 
\begin{document}  
\name{Fanlu Hai \\[12pt]} % the \\[12pt] adds a blank line after name
\address{{\bf Present Address} \\ 37, Broadway west \\ 
York\\ YO10 4JN}
\address{{\bf Email Address} \\ fanlu91@gmail.com \\ {\bf Phone Number} \\
(044)7706 234389
}
\begin{resume} 
\section{Education} 
\section{University of York, UK} 
{\bf Msc in Computing (expecting Merit) } \hfill Sept
2013 -­‐ Jan 2015  \\
\begin{itemize}
  \item Main Coursework: Software
  Measurement and Testing; Software Engineering; Concurrent and Real-Time Java
  Programming; Formal Specification;
\end{itemize}
\section{Zhengzhou University, China}  
{\bf Bsc in Computer Science and Technology } \hfill Sept 2009 -­‐ July 2013\\
\begin{itemize}
\item Main Coursework and Grade: Operating Systems(86);Computer
Organization and Architecture(86); Principle of Database System(85); Data
Structures and Algorithms(76); Network Practical Technology(84); Embedded
Systems(92)
\end{itemize}
\section{Projects}
{\bf Web-based Voting System} \hfill May 2014 -­‐ Sept 2014\\
Msc Dissertation
project. Designed and developed the prototype demonstrator of a web-based voting
system. The project's aim was to optimize the voting procedure in order to
increase user participation, as well as the rationality of results.
\begin{itemize}
  \item Electronic voting system design and implementation. Voting algorithms
  implementation based on voting theory. Specialised server programming.
\item Technologies used
include: Java Servlet, JSP, JavaScript, jQuery, css, MySQL Database and Apache
Tomcat.
\end{itemize}
{\bf JOrtho Testing}\hfill April 2014\\
Software testing project for JOrtho, a multiple languages spell checker for
Java.
\begin{itemize}
  \item The test covers full
unit testing, integration testing and system testing. Software Testing
Documentation follows IEEE Std 829-1998. 
\item Test environment and tools: JDK1.7, JOrtho(version 1.0), Eclipse 4.3.0,
Junit 4, mockito-all-1.9.5.
\item Two major bugs that can cause functional problem were captured by the test
cases.
\end{itemize}
%{\bf A Hotel Keycard-lock System} \hfill March 2014\\
%Using formal specifications, the project successfully created a model that
% could handle lock and key status updates of non-networked door locks, as well as track the activities of the guests.
%\begin{itemize}
%   \item The project used the notation of the formal specification language Z.
   % Programming Tool: ProB.
%   \item Two different solutions were developed. One of them was appraised by
   % the module’s professor as perfect.
% \end{itemize}
{\bf Dialogue Based Tutorial System} \hfill Feb 2014 -­‐ Mar 2014\\
Group project in collaboration with students of various nationalities. Developed a user friendly digital dialogue system for use by university tutors to conduct tutorials for a small group of students.
\begin{itemize}
  \item Use of development life cycle models, software engineering methods and UML tools for requirements analysis and detailed design. Development using java and XML.
  \item Full participation in the project, responsible for the code implementation.
\end{itemize}
{\bf Online Examination system} \hfill Mar 2013 -­‐ June 2014\\
Designed and developed an online examination platform that enables students in
Zhengzhou University to simulate VB/VC language exams. also provided interfaces
for administrators to update data. 
\begin{itemize} 
  \item Being used by the university in practical sessions for most
freshmen and sophomore students.
  \item Outstanding BSc graduation project
  \item Technologies used
include: Java Servlet, JSP, JavaScript, CSS, Ms Access Database and Apache
Tomcat.
\end{itemize}
\section{Contest Awards}   
{\bf The International Space Apps Challenge 2014}  \hfill Apr 2014
\begin{itemize} \itemsep -2pt
  \item Project: Solving the 'Space Mission Roadmap' challenge, a website
  providing information on exploratory missions to other planets (Mars in our
  prototype, scalable) and objects in the solar system.
  \item My Contribution: Developed and modified application modules based on
  real requirements, implemented the back-end server, collected and
  stored data from team researchers in database and generated a json file for
  the front end.
  \item York local Award, Global Awards Finalist(25/671), top 5 in 'Best Mission
  Concept' category globally.
\end{itemize}
{\bf IOT(Internet of Things) Application Design Contest for
National University Students} \hspace{\fill} Aug 2011\\  
\begin{itemize} \itemsep -2pt
  \item Organized by The
Chinese Institute of Electronics, sponsored by Texas Instruments
   \item Project: Drowning Alarm system. Used to detect dangerous situations
   while swimming. The system consists of wireless hardware, routing and a
   control PC.
   \item My Contribution: team leader; design of the sensor used to detect
   drowning; development of the software for the control PC (using C).
   \item Entered National Final(30/200+) and got Third Prize
 \end{itemize}  
\section{Work Experience}
 {\bf Internship } Neusoft Corporation, Dalian, China \hfill Summer  2012
 \begin{itemize} \itemsep -2pt  % reduce space between items
  \item Participated in a graduation scheme that gave me the opportunity to
  sharpen my skills in programming and database design.I also learned about
  software development life cycles.
 \item Website development using java EE, Oracle Database, HTML, CSS and
 Javascript
 \end{itemize} 
{\bf Campus agent} ChinaHR.com, Zhengzhou, China \hfill  Oct 2012 --- April 2013
\begin{itemize} \itemsep -2pt %reduce space between items
\item Organize everything involved in campus recruitment activities, from campus
advertising communicating with potential candidates, as well as conducting first round recruitment interviews.
\end{itemize}
\section{Skills}
 Experienced in Java project development, good knowledge of JDBC, Servlet, JSP,
 and J2EE.\\
SQL (MySQL, MS Access), JavaScript, HTML5, CSS3, XML, JSON, Git, Tomcat, JOrtho\\
Familiarity with C, Oracle DB, Android, Jquery, Ajax\\
Software Testing (JUnit, mock testing)\\
Software Engineering (Object-oriented analysis \& design, software system
modeling using UML)\\
Formal specifications (Z notation)\\ 
Good with numbers, algorithms and data structures.\\
User-centred Design (heuristics, prototyping, user \& expert evaluation)\\
Microsoft Office (Excel, Word, Powerpoint), \LaTeX
\section{Language} English (fluent), Chinese (native)
\section{Personal} Responsibility, assertiveness, fast learner, team player,
good communication skills.
\section{Hobbies and Interests}
Travelling, football (captain of the Chinese students team of
the university), music, always curious about new things.
\end{resume} 
\end{document} 